Better predictive modeling depends on better understanding of the data and attributes selection. We have to choose between some data mining algorithm. We have chosen data mining as it is very much flexible in predictive modeling. Prediction when the game is in progress is a tough ask and it need finding the best attributes that influence the match outcome. Some research was done previously on predictive modeling in sports like Basketball, Baseball along with Test and One Day International cricket.
In basketball, Bhandari et al.\cite{Bhandari1997} developed a knowledge discovery system and data mining framework for National Basketball Association (NBA). It was aimed to discover several interesting patterns in basketball games. This and related system have been used by several basketball teams over the past decades. Such solutions designed for offline usage and no in game effects were taken care of. There has been some recent works (20) about in-game decision making to find how much time remaining in the game without making any prior prediction model.
There were several works done in cricket. Bailey and Clarke\cite{Bailey} and Sankaranarayanan et al.\cite{Sankaranarayanan} used machine learning approach to predict the result of a one day match depending on the previous data and in game data.
Akhtar and Scarf\cite{Akhtar} used multinomial logistic regression in their work on predicting a outcome of a test matches played between two teams.
Choudhury et al.\cite{Choudhury} used Artificial Neural Network to predict result of a multi team one day cricket tournament depending on the past 10 years data. They used training set in order to model the data in neural network. Again there was no in play effects were taken care of.
For baseball, Ganeshapillai and Guttag\cite{Ganeshapillai} developed a prediction model that decides when to change the starting pitcher as the game progresses. It is very much similar to our work-flow, where they used the combination of previous data and in game data to predict a pitchers performance.
Tulabandhula and Rudin\cite{Tulabandhula} were designed a real time prediction and decision system for professional car racing. Model makes the decision of when is the best time for tire change and how many of them. These works supplied a huge encouragement and informative ideas in our research.
